**Results Template**

### 2021-11-03 1_descriptive.Rmd
added functions, more iv
other HCT measures, lie scale

```{r message=FALSE}
df.plot <- df %>% 
  group_by(ID, condition, instruction) %>% 
  summarise(DT_confidence = mean(DT_confidence, na.rm = TRUE),
            DT_RT = mean(DT_RT, na.rm = TRUE),
            yoni_total = mean(yoni_total, na.rm = TRUE),
            BES_total = mean(BES_total, na.rm = TRUE),
            HCT_accuracy = mean(HCT_accuracy, na.rm = TRUE),
            MAIA_total = mean(MAIA_total, na.rm = TRUE))
```

>>>>

```{r message=FALSE}
df.plot <- df %>% 
  group_by(ID, condition, instruction) %>% 
  summarise(DT_confidence = mean(DT_confidence, na.rm = TRUE),
            DT_RT = mean(DT_RT, na.rm = TRUE),
            yoni_total = mean(yoni_total, na.rm = TRUE),
            BES_total = mean(BES_total, na.rm = TRUE),
            HCT_confidence = mean(HCT_confidence, na.rm = TRUE),
            HCT_accuracy = mean(HCT_accuracy, na.rm = TRUE),
            HCT_awareness = mean(HCT_awareness, na.rm = TRUE),
            MAIA_total = mean(MAIA_total, na.rm = TRUE),
            lie_ability = mean(lie_ability, na.rm = TRUE),
            lie_frequency = mean(lie_frequency, na.rm = TRUE),
            lie_negativity = mean(lie_negativity, na.rm = TRUE),
            lie_contextuality = mean(lie_contextuality, na.rm = TRUE))
```

### 2021-11-03 index.Rmd
added functions, more iv
other HCT measures, lie scale

```{r warning=FALSE, message=TRUE, results='asis'}
library(tidyverse)
library(patchwork)
library(glmmTMB)
library(report)
library(parameters)
library(modelbased)
library(performance)
library(bayestestR)
library(see)

@@

```{r warning=FALSE, message=TRUE, results='asis'}
df <- read.csv("data/data_combined.csv") %>% 
  mutate(ID = as.factor(ID),
         condition = as.factor(condition),
         item = as.factor(item),
         style = as.factor(style),
         instruction = as.factor(instruction))

@@

Notice the `{.tabset}` tag after the section name. This will show the subsections as different tabs (in the [html version](https://realitybending.github.io/TemplateResults/#Descriptive_Stats) only, because the other formats are static).

@@

# Inferential Stats {.tabset}

```{r child=if (fast == FALSE) '2_inferential.Rmd'}
```

>>>>

```{r warning=FALSE, message=TRUE, results='asis'}
library(tidyverse)
library(patchwork)
library(glmmTMB)
library(report)
library(parameters)
library(modelbased)
library(performance)
# library(bayestestR)
# library(see)

@@

```{r warning=FALSE, message=TRUE, results='asis'}
setwd("C:/Users/user/Desktop/Sputnik/2019-23/DeceptionInteroTom")
df <- read.csv("data/data_combined.csv") %>% 
  mutate(ID = as.factor(ID),
         condition = as.factor(condition),
         item = as.factor(item),
         style = as.factor(style),
         instruction = as.factor(instruction))

@@

@@

# Inferential Stats (Experimental) {.tabset}

```{r child=if (fast == FALSE) '2_inferential_expt.Rmd'}
```

# Inferential Stats (Behavioural) {.tabset}

Effect on confidence and RT

```{r child=if (fast == FALSE) '3_inferential_behv.Rmd'}
```

### 2021-11-03 scripts/claudia/data processing.Rmd
added functions, more iv
other HCT measures, lie scale

```{r combine data}
data_combined <- read.csv("deceptiontask_extracted.csv") %>% 
  select(-c(contains("start")|contains("stop"))) %>% 
  left_join(read.csv("yoni_processed.csv")) %>% 
  left_join(read.csv("BES_processed.csv")) %>% 
  select(-c(contains("Q"))) %>% 
  left_join(read.csv("HCT_processed.csv")) %>% 
  left_join(read.csv("MAIA2_processed.csv")) %>% 
  select(-c(contains("Q"))) %>% 
  left_join(read.csv("demo.csv")) %>% 
  select(-c(Name, Matric, HP, Email, Birthday, School, Course, LivedinSG))

>>>>

```{r combine data}
qn <- paste0("Q", 1:40)
data_combined <- read.csv("deceptiontask_extracted.csv") %>% 
  select(-c(contains("start")|contains("stop"))) %>% 
  left_join(read.csv("yoni_processed.csv")) %>% 
  left_join(read.csv("BES_processed.csv")) %>% 
  select(-c(contains(paste0("Q", 0:9)))) %>%
  left_join(read.csv("HCT_processed.csv")) %>% 
  left_join(read.csv("MAIA2_processed.csv")) %>% 
  select(-c(contains(paste0("Q", 0:9)))) %>%
  left_join(read.csv("liescale_processed.csv")) %>% 
  select(-c(contains(paste0("Q", 0:9)))) %>%
  left_join(read.csv("demo.csv")) %>% 
  select(-c(Name, Matric, HP, Email, Birthday, School, Course, LivedinSG))
